An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-22 tech-project/paper.tex
paper changes

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.

Resolve is not just concerned with functional correctness, but also considers as a part of overall program correctness performance and space considerations -- and has mechanisms in the language to formally specify these as well. By having a dynamic memory allocation component, we allow our translated code to not have to make special considerations for a hidden steps in compilation that does static allocation. Instead

The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.

Unsurprisingly, concepts are represented in C by a single header .h listing the various methods

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=.55]{figs/fuse.pdf}
\caption{block fusing}
\end{figure}
\label{fig:fuse}

\section{Conclusion}
In this paper we presented a formally specified driver component in RESOLVE, and a single verified enhancement on this component. We introduced a new keyword that allows users to specify in a flexible and transparent fashion the foundational components of the language over which native RESOLVE realizations may be layered. We presented a revised model of RESOLVE to C code and a dynamic allocation scheme that accompanies this new model. 
%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.

>>>>

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations. Another such consideration includes memory, and decisions on dynamic or static allocation. RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system. Following suit, we will introduce a stack based memory allocator in section \#.

The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#. Unsurprisingly, concepts are represented in C by a single header \texttt{.h}. Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE. Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept. RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.

%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=.55]{figs/fuse.pdf}
\caption{block fusing}
\end{figure}
\label{fig:fuse}
%A stack-based approached to dynamic memory allocation requires a fixed size of memory to be set prior to compilation.
